\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/paper.tex
Fill in missing refs

To evade censors, we must send a plausible SNI value (sending no SNI is
uncommon and easily blocked---only 1\% of TLS connections\nikita{qualify this as being true in a particular sample} do not carry the
SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
a plausible (and corresponding) certificate. Even if we manage to avoid sending
either in the clear, censors could actively probe the server in a
way that would normally elicit a certificate.

@@

\smallskip
\noindent
\emph{Alexa sites} -
An alternative strategy is to use popular sites, such as those from the Alexa
top million~\cite{alexa} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the dark decoy address range, such as
large companies that run their own datacenters and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a dark decoy corresponds to a domain's IP.

@@

Website Fingerprinting~\cite{kNN,kFP,DLFP} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to. WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class. Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class). Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.

>>>>

To evade censors, we must send a plausible SNI value (sending no SNI is
uncommon and easily blocked---study conducted using Colorado University network
infrastructure shows that only 1\% of all TLS connections coming in and out of 
campus do not carry the
SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
a plausible (and corresponding) certificate. Even if we manage to avoid sending
either in the clear, censors could actively probe the server in a
way that would normally elicit a certificate.

@@

\smallskip
\noindent
\emph{Popular sites} -
An alternative strategy is to use popular sites, such as those from the Alexa
top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the dark decoy address range, such as
large companies that run their own datacenters and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a dark decoy corresponds to a domain's IP.

@@

Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to. WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class. Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class). Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.
